A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Tweaked preliminaries, and moved the statement that we're considering INDUCED subgraphs to intro

This paper introduces a new branch and bound algorithm which exploits special
properties of these problems to allow a much faster exploration of the search
space, whilst retaining the filtering and bounding benefits of the constraint
programming approach. We describe the algorithm for the basic maximum common
subgraph problem, and discuss how it may be adapted to handle vertex labels,
edge labels, and the requirement that the found subgraph be connected. We then
present an empirical study of the algorithm, demonstrating that it improves the
state of the art by more than an order of magnitude on the unlabelled variant
of the problem, and showing that it can handle much larger instances than
earlier constraint programming or clique approaches due to lower memory usage.

@@

We initially assume that graphs are unlabelled, undirected and without loops
(\cref{sec:extensions} describes how these restrictions may be relaxed).
The vertex and edge sets of a graph $\graphG$ are denoted $\V(\graphG)$ and $\E(\graphG)$.  The
set of vertices adjacent to vertex $v$ in graph $\graphG$ is called the
\emph{neighbourhood} of $v$, denoted $\N(\graphG, v)$. We denote by $\invN(\graphG, v)$ the
\emph{inverse neighbourhood} of $v$, being the set of the vertices not adjacent
to $v$ (excluding $v$ itself). A \emph{subgraph} of a graph $\graphG$ is a graph
consisting of some of the vertices of $\graphG$, and all of the edges between these
vertices. A \emph{common subgraph} of two graphs is a graph which is
(isomorphic to) a subgraph of two graphs simultaneously, and a \emph{maximum}
common subgraph is one with as many vertices as possible. (In this paper, all
subgraphs are induced. The \emph{maximum common partial subgraph} problem
instead asks for a common non-induced subgraph with as many \emph{edges} as
possible \citep{DBLP:conf/cp/NdiayeS11}.)

>>>>

This paper considers the \emph{maximum common induced subgraph} problem, in
which the objective is to find a graph with as many vertices as possible which
is an induced subgraph of each of two input graphs.  (The \emph{maximum common
partial subgraph} problem instead asks for a common non-induced subgraph with
as many \emph{edges} as possible \citep{DBLP:conf/cp/NdiayeS11}.) We introduce
a new branch and bound algorithm which exploits special properties of the
problem to allow a much faster exploration of the search space, whilst
retaining the filtering and bounding benefits of the constraint programming
approach. We describe the algorithm for the basic maximum common subgraph
problem, and discuss how it may be adapted to handle vertex labels, edge
labels, and the requirement that the found subgraph be connected. We then
present an empirical study of the algorithm, demonstrating that it improves the
state of the art by more than an order of magnitude on the unlabelled variant
of the problem, and showing that it can handle much larger instances than
earlier constraint programming or clique approaches due to lower memory usage.

@@

We initially assume that graphs are unlabelled, undirected and without loops
(\cref{sec:extensions} describes how these restrictions may be relaxed).  The
vertex and edge sets of a graph $\graphG$ are denoted $\V(\graphG)$ and
$\E(\graphG)$.  The set of vertices adjacent to vertex $v$ in graph $\graphG$
is called the \emph{neighbourhood} of $v$, denoted $\N(\graphG, v)$. We denote
by $\invN(\graphG, v)$ the \emph{inverse neighbourhood} of $v$, being the set
of the vertices not adjacent to $v$ (excluding $v$ itself). A \emph{subgraph}
of a graph $\graphG$ is a graph consisting of some of the vertices of
$\graphG$, and all of the edges between these vertices. (All subgraphs in this
paper are induced subgraphs.) A \emph{common subgraph} of two graphs is a graph
which is (isomorphic to) a subgraph of two graphs simultaneously, and a
\emph{maximum} common subgraph is one with as many vertices as possible.
